TENDOR-BASED DICTIONARY LEARNING FOR FRAUD DETECTION FROM UNBALANCED DATA

### 2019-02-14 docs/papers/2018ICASSP/2018icassp.tex
updating after backup recovery

% Title.
% ------
\title{TENDOR-BASED DICTIONARY LEARNING FOR FRAUD DETECTION FROM UNBALANCED DATA}
%
% Single address.
% ---------------
\name{Thiago P. de B. Vieira and Jo\~ao Paulo C. L. da Costa}
\address{University of Bras\'ilia}

@@

\section{Introduction}
\label{sec:introduction}
Dictionary Learning is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

% There are two major approaches for dictionary learning. First is the analytic approach, in which DCT bases, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary. In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance. In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively:

@@

@@

@@

@@

@@

>>>>

% Title.
% ------
{Tensor-based Discriminative Sensing for Fraud Detection}
%
% Single address.
% ---------------
\name{Thiago P. de B. Vieira and Jo\~ao Paulo C. L. da Costa}
\address{University of Bras\'ilia}

@@

\section{Introduction}
\label{sec:introduction}

Compressive sensing is emergent for signal processing and hás been applied to Fields such as signal restoration, image processing and classification (sparce representation classification src )

Iterative dictionary learning hás been used as a blind technique for feature extraction, improving classification without require feature selection or principal conponent analysis

Big data analytics require techniques to Deal with multidimensional data, making Sense of strucutre and relationship of many dimensios. Pca is commonly adopted for dimensionality reduction and feature extraction. Tensor hás been adopted for multidimensional data analysis and can be explored for dictionary learning

Adaptive techniques for high dimensional and high thoughput

we propose to apply the tensor deconposition for dictionary learning in order to evidentiate the discriminative sensing of a fraud detection dataset

Dictionary Learning is a signal processing technique for sparse representation of signals as basis vectors, learning the representations from training data, as dictionaries. The sparse representation in terms of such dictionaries has attracted increased interest for compressive sensing and for solving problems such as denoising, compression, image processing, data decomposition, feature extraction and classification \cite{tosic2011dictionary, zhang2010discriminative, zhu2016coupled,ravishankar2011mr}.

% There are two major approaches for dictionary learning. First is the analytic approach, in which DCT bases, wavelets, curvelets and other nonadaptive functions are used as atoms to construct the dictionaries. Second is the learning-based approaches, such as the unsupervised learning for dictionary construction [9] and the online dictionary learning [11], [10], which use machine learning methods to construct the dictionary. In the analytic approach, some pre-defined functions are used to construct the dictionary. Curvelets [24], which tracks the shape of the discontinuity set, offers efficient and near-optimal representation of smooth objects. Shearlets [25], which is obtained from dilations, action of translations and shear transformations, has nice geometric properties and mathematical properties for image representation. Bandelets [26], which specifies the geometry as a vector field, is de-signed to improve the image compression and noise reduction performance. In the learning-based approach, machine learning methods are used to construct the dictionary from the training data. The least square error is used by the method of the optimal directions (MOD) [27] to update the dictionary iteratively:
% Dictionaries are either available analytically, or can be learned from a suitable training set. While analytic dictionaries permit to capture the global structure of a signal and allow a fast implementation, learned dictionaries often perform better in applications as they are more adapted to the considered class of signals.

@@

% In imagery, the numerical burden for (i) learning a dictionary and for (ii) employing the dictionary for reconstruction tasks only allows to deal with relatively small image patches that only capture local image information. Separable dictionaries aims at overcoming these drawbacks by allowing a separable structure on the dictionary throughout the learning process. On the one hand, this permits larger patch-sizes for the learning phase, on the other hand, the dictionary is applied efficiently in reconstruction tasks. The crucial idea is to allow the dictionary to have a separable structure, where separable means that the dictionary D is given by the Kronecker product of two smaller dictionaries A ∈ R h×a and B ∈ R w×b
% Without loss of generality we choose square image patches with w = h = 8, which is in accordance to the patch-sizes mostly used in the literature

@@

\section{Related Works}

Face recognition...

Fisher...

Florian...

Tem que ver outro...

@@

Imbalance data where zero is predominante

Data divided into learning and test, with isfraud labels with 1 or 0

@@

roc_auc is usually used for classification evaluation, but It os not the best option for imbalance data, and Also because It does not consider the unclassified cases, such as false negatives

Due to the inherent complex characteristics of imbalanced data sets, learning from such data requires new understandings, principles, algorithms, and tools to transform vast amounts of raw data efficiently into information and knowledge representation.

We adopt precision recall curve and compare with logistic regression based on original and pca data

Classification based on reconstruction or other value, such as similarity analysis

Evaluate what metric is more discriminative, mse, tsnr or other

@@

The importance of the right metric for classification of imbalanced data

Tensor based analysis explores the extructure and relationship of multidimensional data and can improve the discriminative power of imbalanced data for classification

Can be used for feature extraction and used for well known algorithm,  and can be used for discriminative classification based on heuristics

Our proposal is better for imbalanced data than others techniques
